WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2021-01-03 results/sec_2-workload.tex
Finalized WDIAS Thesis

\cref{fi:test_prod_throughtput_shaping_timer} shows the throughput shaping timer configurations that we used for the load testing, and it is similar to the load test plan described in \cref{se:test_plan}. The maximum peak load that can be had during the load test is 300 \acrshort{rps} (equivalent to 18,000 requests per minute). The following the test plans that we used during the performance testing:

\begin{itemize}
    \item User-defined variables
    \item Setup thread group
    \item Create timeseries thread group
    \item Create extensions thread group
    \item Load test timeseries concurrency thread group
    \item Load test timeseries concurrency thread group
    \item Test flow thread group
\end{itemize}

@@

\begin{itemize}
    \item HTTP request defaults
    \item HTTP header manager
    \item Timeseries metadata CSV
    \item Create timeseries
    \item Get timeseries
    \item Query timeseries
\end{itemize}

@@

\begin{itemize}
    \item HTTP request defaults
    \item HTTP header manager
    \item Timeseries metadata CSV
    \item If scalar or vector then insert timeseries, otherwise insert grid timeseries
    \item Wait for extensions timeseries
    \item Interest area preprocessor
    \item Query if scalar or vector
    \item If scalar or vector then retrieve timeseries, otherwise retrieve grid timeseries
    \item Increment date
    \item Throughput shaping timer prod
\end{itemize}

@@

\begin{itemize}
    \item HTTP request defaults
    \item HTTP header manager
    \item Locations CSV
    \item Interest area preprocessor
    \begin{itemize}
        \item /Location: * $\rightarrow$ Locations
    	\item /Location: Area $\rightarrow$ Locations
    	\item /Parameter: Location $\rightarrow$ Parameters
    	\item /Parameter: Locations $\rightarrow$ Parameters
    	\item /Timeseries: Location $\rightarrow$ Timeseries
    	\item /Timeseries: Locations $\rightarrow$ Timeseries
    	\item /Timeseries: Locations, Parameter $\rightarrow$ Timeseries
    	\item /Timeseries: Area $\rightarrow$ Timeseries
    	\item /Timeseries: Area, Parameter $\rightarrow$ Timeseries
    	\item /Timeseries: *, Parameter $\rightarrow$ Timeseries
    	\item /Timeseries: * $\rightarrow$ Timeseries
	\end{itemize}
\end{itemize}

>>>>

\cref{fi:test_prod_throughtput_shaping_timer} shows the throughput shaping timer configurations that we used for the load testing, and it is similar to the load test plan described in \cref{se:test_plan}. The maximum peak load that can be had during the load test is 300 \acrshort{rps} (equivalent to 18,000 requests per minute). The followings are the test plans that we used during the performance testing:

\begin{itemize}
    \item User-defined variables such as for change variable size 
    \item Setup thread group for test setup before load testing
    \item Create timeseries thread group for create timeseries metadata before import and export timeseries data
    \item Create extensions thread group for create triggers for basic extensions
    \item Load test timeseries with concurrency thread group
\end{itemize}

@@

\begin{itemize}
    \item Load the timeseries metadata CSV
    \item Create timeseries
    \item Check with get timeseries
    \item Query for timeseries
\end{itemize}

@@

\begin{itemize}
    \item Load the timeseries metadata CSV
    \item If scalar or vector then insert relevant timeseries data, otherwise insert grid timeseries data
    \item Wait for extensions timeseries
    \item Query for timeseries metadata
    \item If scalar or vector then retrieve timeseries data, otherwise retrieve grid timeseries data
    \item Increment date
\end{itemize}

@@

\begin{itemize}
    \item Load the locations CSV
    \item Prepare interest area for search for the timeseries
    \begin{itemize}
        \item /Location: * $\rightarrow$ Locations
    	\item /Location: Area $\rightarrow$ Locations
    	\item /Parameter: Location $\rightarrow$ Parameters
    	\item /Parameter: Locations $\rightarrow$ Parameters
    	\item /Timeseries: Location $\rightarrow$ Timeseries
    	\item /Timeseries: Locations $\rightarrow$ Timeseries
    	\item /Timeseries: Locations, Parameter $\rightarrow$ Timeseries
    	\item /Timeseries: Area $\rightarrow$ Timeseries
    	\item /Timeseries: Area, Parameter $\rightarrow$ Timeseries
    	\item /Timeseries: *, Parameter $\rightarrow$ Timeseries
    	\item /Timeseries: * $\rightarrow$ Timeseries
	\end{itemize}
\end{itemize}

### 2021-01-03 summary/sec_1-conclusions.tex
Added news abbr
Finalized WDIAS Thesis

To enhance the accuracy of the weather forecast, we need to provide reliable and timely weather data for \acrshort{nwm}s. Also, most of the existing weather data integration systems are based on basic client-server architectures or monolithic distributed system architectures or developed based on the best technology available at the time of developing those systems. However, most of the concepts are outdated with the technology advancement, and we cannot get the full advantage of modern computational models such as containerized applications and using the cloud computing to gain benefits of scalability, high availability, and low-cost operations. Even though there are many weather data integration systems, most of them are proprietary or closed source. Thus, for an island like Sri Lanka that has different kinds of weather seasons yearly, those software needs to be highly customize.

In this research, we proposed an extendable weather data integration and assimilation system known as \acrfull{wdias}. \acrshort{wdias} focuses on providing a system to efficiently integrate weather data from different sources with supporting quality control. Furthermore, the proposed system is compatible with current cloud computing technologies, architecture patterns, and compatible with modern cloud computing architectures.

>>>>

To enhance the accuracy of the weather forecast, we need to provide reliable and timely weather data for \acrshort{nwms}. Also, most of the existing weather data integration systems are based on basic client-server architectures or monolithic distributed system architectures or developed based on the best technology available at the time of developing those systems. However, most of the concepts are outdated with the technology advancement, and we cannot get the full advantage of modern computational models such as containerized applications and using the cloud computing to gain benefits of scalability, high availability, and low-cost operations. Even though there are many weather data integration systems, most of them are proprietary or closed source. Thus, for an island like Sri Lanka that has different kinds of weather seasons yearly, those software needs to be highly customize.

In this research, we proposed an extendable open source weather data integration and assimilation system known as \acrfull{wdias} \cite{KarunarathneWeatherCode}. \acrshort{wdias} focuses on providing a system to efficiently integrate weather data from different sources with supporting quality control. Furthermore, the proposed system is compatible with current cloud computing technologies, architecture patterns, and compatible with modern cloud computing architectures.
